An emerging approach for cloud correction and filtering of operational microwave humidity radiances

### 2020-09-11 Article/ici_submm_cloudcorr.tex
added QRNN output example

%% 2-column papers and preprints
\documentclass[amt, manuscript]{copernicus}

@@

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range. The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models. ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz. Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization. While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization. 
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_channels}.

\subsection{ICI simulations}
\label{sec:arts_simulations}
%

**** Some parts copied directly from AWS report *****

**** show any comparsion to ATMS? or AWS channels ? ****

\subsection{QRNN}
%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimise the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).

\subsubsection{Model selection}
%
\label{model_selection}
A high performing QRNN model requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-paramter tuning. In grid search, different combinations of hyperparamters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. The model evaluation metrics employed in this article are described in the next section.

@@

\section{Cloud correction in  183 GHz channels}
%
\subsection{Training data}
%
Out of the 200\,000 ICI and MWI channel simulations, 150\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T. The target training data is kept noise free. In order to build a robust learning network, random noise is added to the inputs at each training iteration. This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples. The input data is also normalized with mean and standard deviation.
It is assumed for the simulations that the ICI and MWI channels are mapped to a common footprint and resolution. In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
\subsection{Training}
\label{sec:ici_trainin}
%t
\begin{table}[t]
\caption{Summary of the different QRNN models used in the study.}
\label{tab:QRNN_models}
\begin{tabular}{lll}
\tophline
QRNN model & Training inputs & Target \\
\middlehline
QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I1V\\
			& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I2V\\
			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I3V\\
			& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-15\\	
			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-16\\
QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\

\bottomhline
\end{tabular}
\belowtable{} % Table Footnotes
\end{table}
To investigate the performance of training inputs, two QRNN models with different set of training inputs are analysed. In both models, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183\,GHz channel.

@@

@@

\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-simple for channel I2V.}
	\label{fig:}	
\end{figure}

\subsection{Results}
%
%f 
\begin{figure}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
	\label{fig:PDF_predictions}	
\end{figure}
%f 
\begin{figure}[t ]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' refers to the dataset where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distributions}	
\end{figure}

@@

%t
\begin{table}[t]
	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-simple.}
	\label{tab:statistics_mwi}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &   		 All &   Filtered(5\,K) & Filtered(15\,K) \\
		\middlehline
 MWI-15 		&Bias     &    0.00 &         -1.19 &           -0.02 &                -0.01(4.41\%) & -0.02(1.87\%)\\
				&MAE      &    0.64 &          1.66 &            0.56 &                 0.49 		 &  0.52\\
				&STD      &    0.80 &          6.21 &            0.84 &                 0.64 		 &  0.69\\
				&Skewness &   -0.02 &         -9.87 &           -1.67 &                -0.29 		 & -0.47\\
		\middlehline
 MWI-16 		& Bias 	   &    0.00 &         -0.80 &           -0.04 &   -0.03(2.85\%) & -0.04(1.15\%)\\
				& MAE      &    0.64 &          1.31 &            0.54 &     0.49		 & 0.51\\
				& STD      &    0.80 &          5.01 &            0.82 &     0.63		 & 0.67\\
				& Skewness &    0.01 &        -12.04 &           -1.94 &    -0.23		 &-0.81\\
		\bottomhline			
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
QRNN predictions are estimates of the posterior distribution over different quantiles: $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). To assess the accuracy of the predictions, the median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. The prediction errors are calculated as the deviation of the predictions to their corresponding noise-free clear-sky values. We calculate the mean bias, mean absolute error and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. In the next sections, we describe the performance of the two QRNN models for ICI and MWI channels.

\subsection{Prediction accuracy}
%
The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}. The distributions of corresponding clear-sky simulations are also plotted as reference. The three figures correspond to channels: I1V, I2V and I3V. These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails, where QRNN seems to predict slightly colder/warmer TBs.

@@

\subsection{Uncertainty quantification}
%
%f 
\begin{figure}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-simple for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins_I1V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-simple and QRNN-all for channel I2V. }
	\label{fig:calibration_I2V}	
\end{figure}
The biggest advantage of using QRNN is estimation of case-specific uncertainties. The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates. The predictions for each quantile can be used to construct the confidence intervals. The confidence interval for each point estimate quantifies it's uncertainty. For example, if $\tau_1$ and $\tau_2$ are two quantiles then there is $\tau_2-\tau_1$ probability that the true value will lie in between the range.

@@

\section{Special case of using only 325\,GHz for cloud correction}
In this section, we investigate the possibility of using only channels around
325\,GHz for cloud correction at 183\,GHz. This special case of utilising only
325\,GHz channel can be relevant for smaller satellite missions like Artic
Weather Satellite (AWS) where higher sub-mm channels are not available.

\subsection{Data}
\subsubsection{Artic Weather Satellite}
%t
\begin{table}[t]
	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrr}
		\tophline
		Channel & Frequency 	& Bandwidth  \\
		& [GHz]			& [MHz]		\\
		\middlehline
		AWS-32	&	176.311    & 2000 		\\
		AWS-33	&	178.811    & 2000 		\\
		AWS-34	&	180.311    & 1000 		\\
		AWS-35	&	181.511    & 1000 		 \\
		AWS-36	&	182.311    & \phantom{0}500 	 \\
		AWS-41    & 325.15$\pm$6.60    & 2800 \\
		AWS-42    & 325.15$\pm$4.10    & 1800  \\
		AWS-43    & 325.15$\pm$2.40    & 1200 \\
		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

% Let's try avoid citing the AWS report. If we do, we must put it on
% research.chalmers.se

\subsubsection{AWS simulations}
The satellite observations for AWS channels were simulated with ARTS. An similar ARTS set-up, as described for ICI (Sect.~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle. 125\,000 cases based on randomly selected CloudSat orbits were simulated.
\subsection{Training}
%
Out of the 125\,000 AWS simulations, 75\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. A similar data augmentation technique as described for ICI (Sec~\ref{sec:ici_training}) was followed to build a robust database and avoid memorisation of the samples.

For each 183\,GHz channel from AWS, a training scheme similar to QRNN-simple is used. For example, to
predict clear-sky TBs from AWS-34, the training data includes measurements AWS-34 and channels AWS-41, AWS-42, AWS-43, AWS-44. A grid search over the hyper-parameters was performed (results not shown) and the best performance over the validation set was obtained for 4 hidden layers with 128 neurons and batch size of 128 samples. Rectified Linear Unit (ReLU) was used as the activation function
\subsection{Prediction accuracy}
%f
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/AWS-34_single.pdf}	
	\caption{Error distributions for AWS-34 predictions. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' and  ``predicted(15\,K)''  refers to the datasets where cases with cloud correction greater than 5\,K and 15\,K are excluded, respectively.}
	\label{fig:qrnn_C34_deviations}	
\end{figure}
In an analogy between the results from ICI channels, we perform a similar error distribution analysis. Fig.~\ref{fig:qrnn_C34_deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34. The statistics corresponding to curves are provided in Table~\ref{tab:statistics_qrnn_aws}. The label ``Filtered'' represents the subset where all cases with correction greater than 5\,K(15\,K) are removed. The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.30), however the  error distributions for the predictions are relatively symmetric. Removing cases with cloud correction greater than 5\,K, removes only 3.02\% of the data, but the errors reduce significantly. Infact, the standard deviation of predictions suggests that QRNN is successful in predicting the variability of noise-free simulations.

@@

\section{Outlook and Conclusions}  %% \conclusions[modified heading if necessary]

>>>>

%% 2-column papers and preprints
\documentclass[amt, manuscript]{copernicus}
%\documentclass[amt]{copernicus}

@@

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}

	\belowtable{} % Table Footnotes
\end{table*}

Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range. The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models. ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz. Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization. While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization.

\subsection{MicroWave Imager}
%
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_channels}.

\subsection{Artic Weather Satellite}
%
\begin{table}[t]
	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrr}
		\tophline
		Channel & Frequency 	& Bandwidth  \\
		& [GHz]			& [MHz]		\\
		\middlehline
		AWS-32	&	176.311    & 2000 		\\
		AWS-33	&	178.811    & 2000 		\\
		AWS-34	&	180.311    & 1000 		\\
		AWS-35	&	181.511    & 1000 		 \\
		AWS-36	&	182.311    & \phantom{0}500 	 \\
		AWS-41    & 325.15$\pm$6.60    & 2800 \\
		AWS-42    & 325.15$\pm$4.10    & 1800  \\
		AWS-43    & 325.15$\pm$2.40    & 1200 \\
		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

\subsection{QRNN}
%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimise the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN). 
\subsubsection{Theory}

@@

\subsection{Simulations}
\label{sec:arts_simulations}
%
\subsubsection{Input data}
\subsubsection{Simulation setup}
\subsubsection{Produced dataset}
**** Some parts copied directly from AWS report *****

The satellite observations for AWS channels were simulated with ARTS. An similar ARTS set-up, as described for ICI (Sect.~\ref{sec:arts_simulations}) was followed, except that 24 monochromatic frequencies were used so that each channel could be represented with sufficient accuracy. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle. 125\,000 cases based on randomly selected CloudSat orbits were simulated.

\section{Results}

\begin{table}[t]
	\caption{Summary of the different QRNN models used in the study.}
	\label{tab:QRNN_models}
	\begin{tabular}{lll}
		\tophline
		QRNN model & Training inputs & Target \\
		\middlehline
		QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I1V\\
		& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I2V\\
		& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I3V\\
		& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-15\\	
		& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-16\\
		QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
		& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
		& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\

		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

\subsection{QRNN network configuration and training}
%
\label{model_selection}
A high performing QRNN model requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-paramter tuning. In grid search, different combinations of hyperparamters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. The model evaluation metrics employed in this article are described in the next section.

To investigate the performance of training inputs, two QRNN models with different set of training inputs are analysed. In both models, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183\,GHz channel.

@@

For each 183\,GHz channel from AWS, a training scheme similar to QRNN-simple is used. For example, to
predict clear-sky TBs from AWS-34, the training data includes measurements AWS-34 and channels AWS-41, AWS-42, AWS-43, AWS-44. A grid search over the hyper-parameters was performed (results not shown) and the best performance over the validation set was obtained for 4 hidden layers with 128 neurons and batch size of 128 samples. Rectified Linear Unit (ReLU) was used as the activation function

@@

\begin{figure*}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-simple for channel I2V.}
	\label{fig:}	
\end{figure*}

\subsection{ICI}
\subsubsection{Example results}
%
QRNN predictions are estimates of the posterior distribution over different quantiles. For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The quantiles are interpreted as probabilitic predictions and can be used to construct a probability distribution of the predictions. This is in sharp contrast to other correction approaches which give out only point estimates. Also, the probability distribution can be used to interpret the confidence intervals. For a given case, if two quantiles $\tau_1$ and $\tau_2$ are chosen, then there is $\tau_2 - \tau_1$ chance that the true value ($y_o$) shall lie in in range $[y_{\tau_2}, y_{\tau_1}]$. For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_1 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$.

As an example, Fig.~\ref{fig:posterior_distribution_I2V} shows the posterior distribution obtained from QRNN for three different cases. These results are from QRNN-single for channel I2V. The three cases shown in the figure have almost a similar median value but very different spread for other quantile levels. The spread of the distributions can also be expressed as the prediction interval. If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval. It is gives the range where the prediction could be located and its length is used as a measure of the reliability. The blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability. While the other two cases have longer intervals implying higher fluctuations, or low reliability. Thus, even if two point estimates are highly accurate, or have identical confidence level they could have different uncertainties. The uncertainty quantification is discussed in more detail in Sect.~\ref{sec:prediction_uncertainty}.

%f
\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
	\caption{Posterior distribution obtained from QRNN-single (channel I2V) for three different cases. }
	\label{fig:posterior_distribution_I2V}	
\end{figure}

\subsubsection{Error of best estimate}
%
%f
\begin{figure}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
	\label{fig:PDF_predictions}	
\end{figure}
%f 
\begin{figure}[t ]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' refers to the dataset where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distributions}	
\end{figure}

@@

%t
\begin{table}[t]
	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-simple.}
	\label{tab:statistics_mwi}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &   		 All &   Filtered(5\,K) & Filtered(15\,K) \\
		\middlehline
 MWI-15 		&Bias     &    0.00 &         -1.19 &           -0.02 &                -0.01(4.41\%) & -0.02(1.87\%)\\
				&MAE      &    0.64 &          1.66 &            0.56 &                 0.49 		 &  0.52\\
				&STD      &    0.80 &          6.21 &            0.84 &                 0.64 		 &  0.69\\
				&Skewness &   -0.02 &         -9.87 &           -1.67 &                -0.29 		 & -0.47\\
		\middlehline
 MWI-16 		& Bias 	   &    0.00 &         -0.80 &           -0.04 &   -0.03(2.85\%) & -0.04(1.15\%)\\
				& MAE      &    0.64 &          1.31 &            0.54 &     0.49		 & 0.51\\
				& STD      &    0.80 &          5.01 &            0.82 &     0.63		 & 0.67\\
				& Skewness &    0.01 &        -12.04 &           -1.94 &    -0.23		 &-0.81\\
		\bottomhline			
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

To assess the accuracy of the predictions, the median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. The prediction errors are calculated as the deviation of the predictions to their corresponding noise-free clear-sky values. We calculate the mean bias, mean absolute error and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. In the next sections, we describe the performance of the two QRNN models for ICI and MWI channels.

The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}. The distributions of corresponding clear-sky simulations are also plotted as reference. The three figures correspond to channels: I1V, I2V and I3V. These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails, where QRNN seems to predict slightly colder/warmer TBs.

@@

\subsubsection{Uncertainty quantification}
\label{sec:prediction_uncertainty}
%f 
\begin{figure}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-simple for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins_I1V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-simple and QRNN-all for channel I2V. }
	\label{fig:calibration_I2V}	
\end{figure}
The biggest advantage of using QRNN is estimation of case-specific uncertainties. The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates. The different quantiles provide the measure of possible fluctuations in the prediction, also known as confidence interval. 
The
predictions for each quantile are used to construct the confidence intervals.
The confidence interval for each point estimate is a way to quantify its
uncertainty. For example, the predicted quantiles for $\pm 1 \sigma$ give 68\%
probability that the true value will lie between the range.

@@

\subsection{MWI}
\subsubsection{MWI alone}
\subsubsection{MWI and ICI}

\subsection{AWS}
In this section, we investigate the possibility of using only channels around
325\,GHz for cloud correction at 183\,GHz. This special case of utilising only
325\,GHz channel can be relevant for smaller satellite missions like Artic
Weather Satellite (AWS) where higher sub-mm channels are not available.

Out of the 125\,000 AWS simulations, 75\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. A similar data augmentation technique as described for ICI (Sec~\ref{sec:ici_training}) was followed to build a robust database and avoid memorisation of the samples.

\subsection{Prediction accuracy}

%f
\begin{figure}[t]
	\includegraphics[width = 80mm]{Figures/AWS-34_single.pdf}	
	\caption{Error distributions for AWS-34 predictions. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' and  ``predicted(15\,K)''  refers to the datasets where cases with cloud correction greater than 5\,K and 15\,K are excluded, respectively.}
	\label{fig:qrnn_C34_deviations}	
\end{figure}
In an analogy between the results from ICI channels, we perform a similar error distribution analysis. Fig.~\ref{fig:qrnn_C34_deviations} shows the error distributions of the measurements and predicted clear-sky TBs for AWS-34. The statistics corresponding to curves are provided in Table~\ref{tab:statistics_qrnn_aws}. The label ``Filtered'' represents the subset where all cases with correction greater than 5\,K(15\,K) are removed. The cloud impact in the uncorrected measurements is reflected in the high negative skewness (-10.30), however the  error distributions for the predictions are relatively symmetric. Removing cases with cloud correction greater than 5\,K, removes only 3.02\% of the data, but the errors reduce significantly. Infact, the standard deviation of predictions suggests that QRNN is successful in predicting the variability of noise-free simulations.

@@

\section{Discussion}
\section{Outlook and Conclusions}  %% \conclusions[modified heading if necessary]
